Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-09-24 paper/paper.tex
More ideas

An early graph database system by \citet{DBLP:conf/pods/ShashaWG02} uses a filtering heuristic to
eliminate unsatisfiable instances based upon simple structural elements. It is not clear whether the
aim is to reduce I/O costs, or to reduce the number of queries which must be tested, and the
experiments do not answer whether the indexing is effective. (?? This isn't the first paper on this,
but before this seem to be commercial applications, in particular a system called Daylight. Maybe
more digging is required.)

@@

Read outside the field. AI has a lot to offer. Much more focus on the matching algorithm.

?? Optimisations for trivial cases. Lazy forward checking, cheap alternatives to heuristics and
all-different. Presolving.

?? Invariant which are effective on labels used to inform algorithm design and to provide filtering
during search. Minimum unsat core. Indexing can be used to enhance propagation.

>>>>

An early graph database system by \citet{DBLP:conf/pods/ShashaWG02} uses a filtering heuristic to
eliminate unsatisfiable instances based upon simple structural elements. It is not clear whether the
aim is to reduce I/O costs, or to reduce the number of queries which must be tested, and the
experiments do not answer whether the indexing is effective. However, the work was influenced by a commercial
graph database system, whose documentation \cite[section 7.1]{Daylight} states that indexing is
used to minimise disk accesses.

@@

?? They need to read outside the field. AI has a lot to offer. There needs to be much more focus on
the matching algorithm, and how it interacts with the system as a whole.

?? We need optimisations for trivial cases. Lazy forward checking, cheap alternatives to heuristics and
all-different. Presolving. Huge domains.

?? Degrade to clique.

?? Invariant which are effective on labels used to inform algorithm design and to provide filtering
during search. Look at minimum unsat core. If we are prepared to spend hours, indexing-like system
can be used to enhance propagation, for example by pre-computing degree sequences and paths on
target graphs. This is stronger, because, say, counting red vertices and counting degrees are
automatically combined.
